

\documentclass{resume} % Use the custom resume.cls style

%\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Carlyn Lee} % Your name
\address{carlyn.lee@gmail.com \\
626-372-4206} % Your phone number and email
\begin{document}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Technical Strengths}

%\center{C/C++, C\#, Java, Python, Javascript, Matlab, Visual Basic, Excel, MEAN.io, OpenCV, OpenGL}

%\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
\begin{rSubsection}{Jet Propulsion Laboratory, California Institute of Technology}{August 2012 - Present}{Applications Software Engineer}{Pasadena, CA}
\item  Parallel channel coding simulations and high-res az-el terrain mask algorithm development on Cray XC40. Integration and development of Link Performance \& SNR calculation and Data Volume modeling tools for concurrent link analyses in M2020 Relay Telecom Predictor.

\item Communications support for collaborative multi-agent autonomy in maritime and subterranean environments. V\&V for  software on networked Raspberry Pi's and unmanned surface vehicles.  Trade studies and implementation of radio mesh network in mining tunnel contributed to 1st place win in DARPA's Subterranean Challenge Urban Circuit. Ultra-wide band ROS integration to improve robot localization in GPS/comm deprived environments.

\item Developed intelligent interfaces for DSN operators and telecom engineers to increase efficiency of operator support to NASA deep-space missions. Implemented framework for Link Complexity and Maintenance software to query events \& trends from Sequence of Events files and estimate a link complexity profile. Architected data delivery systems for DSN downlink streams to reduce rover operation response-time to requirement of 20 minutes. Using Tableau \& Web Data Connectors, Kibana aggregated data and event anomalies flagged by rules-engine and Event Verification Records \& Engineering Housekeeping, and Accountability data. 

\item Telecom forecast prediction tools for various deep space missions, including full web stack development for SaaS application prototype. Implementation of network link models. Spacecraft, planetary, camera-matrix, and events analysis using C/C++. UX development for scheduling telecom links, e.g. Liferay portlet, Drupal, D3, WebGL. 
\item Modeling of communications traffic flow for human exploration of Mars \& Moon. Python implementation of Markov model for estimating bandwidth requirements in Deep Space Network simulations. 
\item Radio science operator for Cassini Spacecraft. Investigation of atmospheric losses for 32GHz radio communications recorded on Deep Space Network open \& closed loop receivers. Prototyped data warehouse for quick visualization of radio science data from Cassini Spacecraft during 2004-2015. 
\end{rSubsection}

%------------------------------------------------


%----------------------------------------------------------------------------------------
%	VOLUNTEER & PROFESSIONAL AFFILIATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{ Extracurricular, Volunteer \& Professional Affiliations}
Interplanetary Small Satellite Conference Committee, Caltech Alpine Club Website Administrator.\\
{\bf 2020 - present} Foothill Unity Center, Monrovia, CA: Unloaded and packed food to families in need. \\
{\bf Nov 2019 - Feb 2020} Rosebowl Masters Swimming: As a Polar Bear Club Member, completed a minimum of 19 one-hour workouts of the 24 offered during the winter month 2020. \\
{\bf 2019} Member of Duarte Ad Hoc Finance Advisory Committee, appointed by Duarte City Council. \\
{\bf 2010 - 2012} Vice-President of Association for Computing Machinery, CSU Fullerton.\\
{\bf 2000 - 2004} Walnut High School Swimming, four-year letterwinner \& League Champion, All-American Academic Listing, CIF-SS title 100 fly. \\
{\bf 1998 - 2004} Brea Aquatics, Senior Group Swimmer.
 

\end{rSection}



%----------------------------------------------------------------------------------------
%	AWARDS AND HONORS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Certifications}
{\bf } Adult and Pediatric First Aid/CPR/AED, The American Red Cross (Certificate ID 00ISKSO).\\
{\bf } Technician Class Amateur Radio Operator. \\
{\bf } Private Pilot-ASEL +300hrs including instruction in PA28, C152, C172, CT210M.\\

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf California State University, Fullerton}  \\ 
M.S. Computer Science \hfill {\em August 2012}\\
B.S. Computer Science, Minor in Mathematics  \hfill {\em July 2011}\\
\end{rSection}
%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
